Optimizing Abstract Abstract Machines

### 2013-07-05 paper/icfp105-johnson.tex
Small typo.

We thank Suresh Jagannathan for providing source code to the
polymorphic splitting
analyzer~\cite{dvanhorn:wright-jagannathan-toplas98} and Ilya Sergey
for the introspective pushdown
analyzer~\cite{dvanhorn:Earl2012Introspective}.  
%
We thank Sam Tobin-Hochstadt for encouragement and feedback---he was
the first to prompt us to look into how make effective
implementations of the AAM approach.
%
We thank Vincent St-Amour and Mitchell Wand for feedback on early drafts
and Greg Morrisett and Matthias Felleisen for discussions.
%
We thank our anonymous reviewers for their detailed comments.
%
This material is based on research sponsored by DARPA under the
programs Automated Program Analysis for Cybersecurity
(FA8750-12-2-0106) and Clean-Slate Resilient Adaptive Hosts (CRASH).
The U.S. Government is authorized to reproduce and distribute reprints
for Governmental purposes notwithstanding any copyright notation
thereon.

>>>>

We thank Suresh Jagannathan for providing source code to the
polymorphic splitting
analyzer~\cite{dvanhorn:wright-jagannathan-toplas98} and Ilya Sergey
for the introspective pushdown
analyzer~\cite{dvanhorn:Earl2012Introspective}.  
%
We thank Sam Tobin-Hochstadt for encouragement and feedback---he was
the first to prompt us to look into how to make effective
implementations of the AAM approach.
%
We thank Vincent St-Amour and Mitchell Wand for feedback on early drafts
and Greg Morrisett and Matthias Felleisen for discussions.
%
We thank our anonymous reviewers for their detailed comments.
%
This material is based on research sponsored by DARPA under the
programs Automated Program Analysis for Cybersecurity
(FA8750-12-2-0106) and Clean-Slate Resilient Adaptive Hosts (CRASH).
The U.S. Government is authorized to reproduce and distribute reprints
for Governmental purposes notwithstanding any copyright notation
thereon.
